密文重复数据删除机制的频率攻击方法

### 2018-12-12 paper/main.tex
ING | writing introduction over

\documentclass[bachelor]{thesis-uestc}

@@

\section{研究工作的背景与意义}

在本节中，我们将介绍普通和加密重复数据删除方法的基础知识。
我们专注于基于块的重复数据删除，它以称为块的小型数据单元的粒度运行。图1总结了重复数据删除工作流程。具体地，存储系统首先经由一些组块过程将客户端的文件（例如，备份）分割成逻辑组块，使得每个逻辑组块由其内容的加密哈希唯一地标识，称为标签（即，指纹）。如果两个逻辑块具有相同的标记，则认为它们是相同的，而不同逻辑块具有相同标记的可能性几乎可以忽略不计[24]。存储系统仅存储相同逻辑块的副本作为物理块，并且每个相同的逻辑块通过小尺寸引用引用相同的物理块。
基于块的重复数据删除比整个文件重复数据删除更精细，因此通常具有更高的存储效率。我们可以进一步选择固定大小或可变大小的块来进行重复数据删除。固定大小的分块将数据分区为等大小（逻辑）块，而可变大小的分块（也称为内容定义的分块）通常以内容相关的方式指定块边界（例如，通过Rabin指纹[54]）和分区将数据文件转换为可变大小的块。固定大小的分块简单而快速，而可变大小的分块在内容转换时保持存储效率，因为即使文件添加或删除了一些内容，大多数块仍然保持不变。可变大小的分块通常用在备份系统中（例如，[46]，[66]），但固定大小的分块显示对某些工作负载（例如，VM映像[38]）有效。我们的工作涉及固定大小和可变大小的分块方法。
加密的重复数据删除解决了外包环境（例如，云存储）中的块机密性，同时保持了重复数据删除的有效性。传统的对称加密要求多个客户端通过其（不同的）密钥加密其文件数据，从而将相同的块转换为不再能够进行重复数据删除的不同加密块。消息锁定加密（MLE）[21]规范了加密重复数据删除。基线MLE实例化基于每个明文的内容（例如，基于块的重复数据删除中的逻辑组块）导出对称密钥（称为MLE密钥），并使用MLE密钥加密明文以形成密文（例如，加密的逻辑块）。因此，MLE确保将相同的明文加密为相同的密文。最后，存储系统从每个密文中导出标签并执行重复数据删除。

MLE可以实现为不同的实例化（参见第VIII节）。最受欢迎的是融合加密（CE）[29]，它已在各种存储系统中实现（例如，[3]，[5]  -  [7]，[9]，[13]，[15] ]，[28]，[58]）。 CE的主要思想是从每个明文内容的加密散列中导出MLE密钥。注意，一些MLE实例[21]允许将相同的明文加密成不同的密文。然而，他们确保标签仍然来自明文，因此他们可以通过检查标签的相等性来执行重复数据删除。
现有的MLE实例都建立在概念确定性加密的基础上，以确保密文（或标签）确定性地从明文传递，从而保持重复数据删除的有效性，而不是传统的对称加密。虽然确定性加密提供了机密性保证，但在本文中，我们认为攻击者可以利用这种确定性来推断给定密文的原始明文。

\chapter{Introduction}
\label{sec:introduction}

Modern storage systems save storage space by removing content redundancy 
via {\em deduplication}, which stores only the data copies with unique content
among all already stored data copies.  Field studies show that deduplication
effectively saves substantial fractions of storage space for real-world
storage workloads, such as backups
\cite{zhu08,lillibridge09,wallace12,douglis17}, file system snapshots
\cite{meyer11}, and virtual machine (VM) disk images \cite{jin09}.  Cloud
storage services (e.g., Dropbox and Google Drive) also deploy deduplication to
save maintenance costs \cite{harnik10}. 
To ensure data confidentiality, clients should first encrypt their own data
before writing the data to a storage system.  It is critical that the
encryption approach preserves the original content redundancy pattern, so that
duplicate data copies can still be detected and removed from the storage
system even after encryption.

We study {\em encrypted deduplication}, which combines encryption and
deduplication in a way that each plaintext (data copy) is symmetrically
encrypted and decrypted by a key that is derived from the content of the
plaintext itself; in other words, should the plaintexts be duplicates, their
resulting ciphertexts are also duplicates and hence can be deduplicated.
Encrypted deduplication can be achieved through the formal cryptographic
primitive known as {\em message-locked encryption (MLE)} \cite{bellare13a},
whose instantiations have been extensively studied and realized in the
literature (see Section~\ref{sec:background}).  MLE builds on the notion of
{\em deterministic encryption}, which deterministically maps a plaintext to
the same ciphertext to preserve the identical content pattern.  In addition to
MLE, deterministic encryption is also found in symmetric searchable encryption
(SSE) \cite{song00} and order-revealing encryption (ORE) \cite{boldyreva09},
so as to allow efficient queries over encrypted data.

%that yields the same ciphertext for a given plaintext and key, even over
%separate executions of the encryption functions. This makes it specially
%efficient for {\em equality test}, meaning that finding an exact match
%plaintext is as easy as finding an exact match over the corresponding
%ciphertext. Thus, deterministic encryption has been applied in various
%application-specific cryptographic primitives, such as symmetric searchable
%encryption (SSE) \cite{song00}, order-revealing encryption (ORE)
%\cite{boldyreva09} and message-locked encryption (MLE) \cite{bellare13a},
%so as to enable efficient queries over encrypted data.

%the effectiveness of frequency analysis against deterministic encryption in
%the context of {\em deduplication}, which stores only data copies, called
%{\em chunks}, that have unique content among all already stored chunks. The
%deduplication technique can effectively reduce the storage space of different
%workloads (e.g., 68\% for primary data \cite{meyer09}, 83\% for backup data
%\cite{meyer09}, and 80\% for virtual machine volumes \cite{jin09}),
%and it has been deployed in various cloud storage services (e.g., Dropbox
%and Google Drive) for minimizing maintenance cost
%\cite{harnik10}. To protect information, (encrypted) deduplication
%applies deterministic encryption \cite{bellare13a} on each chunk, such
%that the redundant copies of plaintext chunks can  be removed
%efficiently.  Compared to database records \cite{naveed15} or searchable
%keywords \cite{islam12}, the chunks involved in deduplication constitute
%a huge domain (e.g., over ten millions of possible plaintext values), and
%the underlying plaintexts of some target chunks may not appear in the
%auxiliary information. In addition, a large fraction of chunks have the
%same frequencies in practical deduplication workloads \cite{li17}, and
%this fact has been shown to decrease the effectiveness of frequency
%analysis \cite{naveed15}.    Prior work \cite{li17} shows that classical
%frequency analysis can only infer a few plaintext chunks in
%deduplication.

However, because of the deterministic nature, encrypted deduplication leaks
information about the ciphertexts, such that the adversaries can analyze the
ciphertexts and infer their corresponding original plaintexts.  Specifically,
an adversary can perform {\em frequency analysis} \cite{alkadit92} on both the
ciphertexts that are observed and the plaintexts that are known a priori.
Then the adversary can infer the ciphertext-plaintext pairs, in which both the
ciphertext and the plaintext in each pair have correlated frequency patterns. 
Such inference attacks have been shown effective against database records (e.g.,
\cite{lacharite18,grubbs17,kellaris16,naveed15,bindschaedler17,durak16}) and
searchable keywords (e.g., \cite{pouliot16,zhang16b,cash15,islam12,grubbs16})
that are protected by deterministic encryption.   In particular, frequency
analysis is shown to effectively infer plaintext information from encrypted
deduplication \cite{li17}.

In this paper, we revisit the information leakage issues in encrypted
deduplication.  We argue that encrypted deduplication can actually be even
more vulnerable towards carefully crafted frequency analysis attacks.  Such
sophisticated attacks not only infer a significant fraction of
ciphertext-plaintext pairs as shown in the previous work \cite{li17}, but also
ensure that each inferred plaintext indeed corresponds to the target
ciphertext with a high probability.  From a statistical perspective, The
latter implies that the number of false positives is low, or equivalently, the
precision is high.

To this end, we propose {\em two} new frequency analysis attacks against
practical encrypted deduplication storage systems, and demonstrate their
severity using real-world storage workloads.  Both attacks build on the
characteristics of practical deduplication workloads.  While such
characteristics have been exploited to improve deduplication performance and
storage efficiency in practice, we show how to exploit them from an
adversarial perspective.  We hope that our findings help practitioners and
researchers better understand the vulnerabilities in encrypted deduplication
and motivate more research along this direction.

%They exploit the orders and frequencies of plaintexts preserved within a
%sequence of ciphertexts, in order to infer ciphertext-plaintext pairs as many
%as possible.  However, we find the prior attack  introduces a large number of
%false positives into its inference results and has low precision in
%extracting correct information. In other words, while capable of inferring a
%significant fraction of ciphertext-plaintext pairs, it cannot ensure each
%inferred plaintext is exactly mapped from the target ciphertext.

% For example, our evaluation shows although the locality-based attack can correctly infer 15.2\% of ciphertext-plaintext pairs in some case, the false positives take around 65.2\% in its inference results. In other words, the adversary has low confidence in identifying whether the inferred ciphertext-plaintext pairs are correct or not.

% In this paper, we further examine the information leakage issues in encrypted
% deduplication and argue that encrypted deduplication is in fact even more
% vulnerable towards inference attacks.  We show that in addition to exploiting
% the deterministic encryption nature, an adversary can leverage other leakage
% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
% systems.  We propose {\em two} novel inference attacks that extend frequency
% analysis and demonstrate their severity against real-world storage workloads.
% We hope that our findings help practitioners and researchers better understand
% the security issues in encrypted deduplication storage and motivate more
% research along this direction.

%Note that variable-size chunking, chunk locality, and similarity are the key
%design primitives of existing deduplication systems to improve deduplication
%performance and storage savings.  We show how these primitives can be
%exploited from an adversarial perspective. 
% We show that in addition to exploiting
% the deterministic encryption nature, an adversary can leverage other leakage
% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
% systems.  We propose {\em two} novel inference attacks that extend frequency
% analysis and demonstrate their severity against real-world storage workloads.

\section{Overview of New Frequency Analysis Attacks}

We summarize the main ideas of our two new frequency analysis attacks against
encrypted deduplication, namely the {\em distributed-based attack} and the
{\em clustering-based attack}. They build on different assumptions of
adversarial knowledge.

\paragraph{Distribution-based attack:}  The attack builds on the 
{\em locality} property \cite{xia11,lillibridge09,zhu08}, which states that
the ordering of data is likely preserved across various backup files, to infer
the ciphertext-plaintext pairs that are in similar positions of backup files.
In particular, it examines the relative frequency distribution based on the
co-occurrence frequencies of adjacent data, and explores the observation that a
plaintext and its corresponding ciphertext are likely to have similar relative
frequency distributions. Our evaluation shows that the distribution-based
attack reduces the number of false positives of the previously proposed
locality-based attack \cite{li17} by up to 82.4\%, while correctly inferring
up to 21.2\% ciphertext-plaintext pairs (higher than that of the
locality-based attack \cite{li17} by 6\% in the same case).

Furthermore, the distribution-based attack can exploit the leakage of the
varying sizes of plaintexts to filter more false positives.  Our evaluation
shows that it can suppress the fraction of false positives to as low as 1.7\%.

%with {\em variable-size chunking} (see Section~\ref{sec:background}), which partitions file data into smaller units of varying sizes to better remove duplicate content at finer-grained granularities. We leverage the varying sizes of plaintexts to  filter possibly flawed inference results. Our evaluation shows the distribution-based attack further suppresses the fraction of false positives as low as 1.6\%.

% An adversary can leverage the varying sizes of ciphertexts to infer the original plaintexts.  Our evaluation shows that the size-based attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a real-world dataset.

%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
%(see Section~\ref{sec:background}), which partitions file data into smaller
%units of varying sizes to better remove duplicate content at finer-grained
%granularities. An adversary can leverage the varying sizes of ciphertexts to
%infer the original plaintexts.  Our evaluation shows that the size-based
%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
%real-world dataset.

% We also combines 
% This attack exploits the ordering of
% ciphertexts before deduplication and is applicable for both fixed-size and
% variable-size chunking approaches; in other words, we relax the adversarial
% knowledge about the chunk size in the size-based attack.   
% It further inspects the relative frequency distribution of the data
% and filters any potentially flawed inference results.  Our evaluation shows
% that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
% pairs in a real-world dataset, while significantly reducing the number of
% false positives compared to the prior attack \cite{li17}.

\paragraph{Clustering-based attack:}  The attack relaxes the knowledge about
the ordering pattern exploited by the distribution-based attack.  It builds on
the {\em similarity} property \cite{xia11,bhagwat09}, which states that backup
files share a large fraction of the same data (the ordering may not be
preserved), to infer the ciphertext-plaintext pairs that are clustered
in similar regions of a backup file.  Our evaluation shows that the
clustering-based attack infers up to 30.8\% of raw data content in a
real-world VM image dataset.

%group ciphertexts and plaintexts into clusters, respectively. Then, it infers
%the original contents of ciphertexts from the similar clusters of a backup
%file. 
% infer the ciphertext-plaintext pairs that are in similar
% {\em clusters} of a backup file.

\paragraph{Observations:}  We study the nature of our frequency analysis
attacks based on real-world datasets.  In general, the distribution-based
attack preserves the attack severity even when the prior knowledge of
plaintexts is loosely correlated with the ciphertexts to be attacked.  The
reason is that it uses a statistical approach to quantify the relative
frequency distribution and addresses the disturbance to frequency ranking.  This indicates a wide
exploitation of the distribution-based attack, which should be taken into
account when developing countermeasures.   Also, the distribution-based attack
is more likely to affect rarely updated large files (e.g., disk image files)
or some correlated small files (e.g., programming source files) that are stored together, while the clustering-based
attack mainly threatens the confidentiality of VM disk images.

%We summarize the main ideas of our three inference attacks against encrypted
%deduplication.  The inference attacks build on different assumptions of
%adversarial knowledge.

%In this paper, we propose new inference attacks that increase the effectiveness of frequency analysis with {\em various leakages} of practical deduplication. The key technique is based on an extensive exploitation of the characteristics of deduplication workloads, so as to {\color{blue} identify the available auxiliary information  that is highly correlated with  the underlying plaintexts of target chunks}.  We empirically evaluate our attacks based on real-world datasets, and present new observations about the dataset characteristics for which deterministic encryption is especially insecure. We also discuss possible countermeasures to mitigate the leakage channels. In the following, we summarize the main results of this paper.

%\subsection{Overview of Inference Attacks}

%We summarize the main ideas of our three inference attacks against encrypted
%deduplication.  The inference attacks build on different assumptions of
%adversarial knowledge.

%\begin{itemize}[leftmargin=*]
%\item
%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
%(see Section~\ref{sec:background}), which partitions file data into smaller
%units of varying sizes to better remove duplicate content at finer-grained
%granularities. An adversary can leverage the varying sizes of ciphertexts to
%infer the original plaintexts.  Our evaluation shows that the size-based
%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
%real-world dataset. 
%\item
%{\bf Distribution-based attack:}  This attack exploits the ordering of
%ciphertexts before deduplication and is applicable for both fixed-size and
%variable-size chunking approaches; in other words, we relax the adversarial
%knowledge about the chunk size in the size-based attack. It leverages the {\em
%chunk locality} property \cite{xia11,lillibridge09,zhu08}, which states that
%the ordering of data is likely preserved across various backup files, to infer
%the ciphertext-plaintext pairs that are in similar {\em positions} of backup
%files.  It further inspects the relative frequency distribution of the data
%and filters any potentially flawed inference results.  Our evaluation shows
%that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
%pairs in a real-world dataset, while significantly reducing the number of
%false positives compared to the prior attack \cite{li17}. 
%\item
%{\bf Clustering-based attack:}  This attack further relaxes the knowledge
%about the ordering of ciphertexts in the distribution-based attack.  It
%exploits the {\em similarity} property \cite{xia11,bhagwat09}, which states
%that backup files share a large fraction of the same data (the ordering may
%not be preserved), to infer the ciphertext-plaintext pairs that are in similar
%{\em clusters} of a backup file.  Our evaluation shows that the
%clustering-based attack infers up to 18.1\% of ciphertext-plaintext pairs in a 
%real-world VM image dataset.
%\end{itemize}

%Note that variable-size chunking, chunk locality, and similarity are the key
%design primitives of existing deduplication systems to improve deduplication
%performance and storage savings.  We show how these primitives can be
%exploited from an adversarial perspective.

%%Our trace-driven evaluation shows that the distribution-based attack infers up to 21.2\% of plaintext chunks in the FSL dataset. For comparison, with the same auxiliary information, the inferred chunks by the locality-based attack \cite{li17} (that uses the same leakage of logical order) takes a fraction of 15.2\%. Another advantage of the distribution-based attack is that its effectively is less affected by the correlations between the auxiliary information and target chunks. For example, when we use some loosely correlated auxiliary information, this only degrades the coverage of inferred chunks by 1.4\%.

%%distinguish chunks by their sizes.  Specifically, we propose the {\em
%%size-based attack}, whose idea is to group all chunks by their sizes and
%%launch frequency analysis against each group of chunks of the same size.  Our
%%evaluation shows that the size-based attack correctly infers up to 31.3\% of
%%ciphertext-plaintext pairs in a real-world dataset.

%%The distribution-based attack builds on {\em chunk locality}
%%\cite{xia11,lillibridge09,zhu08}, which is the tendency for chunks in backup
%%streams to re-occur together in the same order. Specifically, if a chunk $M$
%%is surrounded by the chunks $M'$ and $M''$ in one backup, then $M$ is likely
%%to be surrounded by $M'$ and $M''$ in future backups. The rationale is that
%%backup updates  cluster together and affect a few regions of chunks, while
%%the remaining large stretch of chunks (in backup streams) remain unchanged.
%%We adapt this characteristics to frequency analysis. Our insight is that if
%%$M$ is the underlying plaintext of a ciphertext chunk $C$, then $M$ and $C$
%%are likely to have similar (relative) frequency distribution on the
%%%co-occurrences of their surrounding chunks. We propose to adjust frequency
%%ranking and filter out unreasonable inference results based on the relative
%%frequency distribution. The distribution-based attack incorporates the
%%(distribution-based) frequency ranking with locality-based loop \cite{li17}
%%to iteratively infer more chunks.

%%The distribution-based attack assumes the leakage of the logical orders of
%%chunks. Specifically, the adversary has the knowledge about the position, in
%%which each chunk appears in the file data before deduplication.

%%In addition to chunk frequencies, we consider the presence of chunk size leakage.  We propose the {\em size-based attack} to extract plaintext information of the chunks yielded by {\em variable-size chunking}, which has already been used in practical systems such as LBFS \cite{muthitacharoen01} and Deep Store \cite{you05} to address boundary-shift problem. Specifically, variable-size chunking computes the Rabin fingerprint \cite{rabin81} based on a sliding window of data content, and places a chunk boundary when the resulting fingerprint matches a specific pattern. In other words, different chunks may have different chunk sizes due to their possibly distinct content patterns. Thus, we group all available chunks by chunk size, and launch frequency analysis through the chunks that have the same size. Our trace-driven evaluation shows that the size-based attack correctly infers up to 31.3\% of plaintext chunks in the real-world FSL dataset (see Section~\ref{sec:dataset}).

%% . In other words, variable-size chunking generate chunks based on original content so as to address the problem of boundary shift. Our insight is different chunks possibly have different sizes in the setting. We can group all available chunks by their sizes, and launch attack on each chunk group, separately.  
%% about the order of each chunk in original input files.
%% that expands threat to both variable-size and fixed-size chunks.

%% Based on the necessary requirement, we propose distribution-based ranking  
% % primitive 
%% adjust the ranking of frequency analysis, and filter out unreasonable
%% inference results. The distribution-based attack     
%%to improve the effectiveness of classical frequency analysis.

%% has an inference precision of 64.7\% to infer up to 21.2\% of original FSL backup data. For comparison, with the same auxiliary knowledge, the prior locality-based attack \cite{li17} achieves the corresponding precision and rate of only 34.8\% and 15.2\%, respectively. Another advantage is that the effectiveness of the distribution-based attack is less affected by the frequency correlations between the auxiliary and target chunks. For example, when we use a less correlated auxiliary dataset, this only leads to a limited inference rate degradation of 1.4\%.

%% In addition, we observe that the distribution-based attack mainly threatens the rarely-update large-size files, and it can infer up to XXX\% of corresponding original content.

%%\paragraph{Attack using generic order:}
%%We consider to relax the required  knowledge of the distribution-based attack. We assume that the adversary learns the (generic) order information in a {\em coarse-grained unit}, in which a number of chunks appear together as a set; while the adversary cannot identify the accurate order of any chunk in each set.   
%%
%%To exploit the (relaxed) adversarial knowledge, we propose the {\em
%%clustering-based attack}, which builds on {\em similarity}
%%\cite{li17,qin17,xia11,bhagwat09}. Specifically, similarity states that two
%%sets of chunks have the same minimum cryptographic hash (i.e., {\em
%%MinHash}) over their elements if and only if they have a large
%%fraction of common chunks \cite{broder97}. Prior approaches
%%\cite{li17,qin17,xia11,bhagwat09} apply similarity to improve the storage
%%efficiency of near-exact deduplication, while we adapt it into inference
%%attack: suppose $S_{\rm a}$ and $S_{\rm t}$ are the sets of plaintext and
%%ciphertext chunks, respectively; our insight is that if the MinHash
%%derived from the underlying plaintext chunks of $S_{\rm t}$ is identical
%%with that of $S_{\rm a}$, then the plaintexts of the ciphertext chunks in
%%$S_{\rm t}$ are likely to be in $S_{\rm a}$.
%%Thus, we can use $S_{\rm a}$ as the auxiliary information, and launch frequency analysis to infer the chunks corresponding to $S_{\rm t}$.
%%
%%The effectiveness of the clustering-based attack depends on how chunks are
%%grouped in each set. We observe that the clustering-based attack is severe for
%%some special workloads, such as the virtual machine (VM) disk images that
%%store data aligned with block boundaries and are commonly chunked into
%%fixed-size chunks for deduplication \cite{jin09}. Our trace-driven evaluation
%%shows that the clustering-based attack infers up to 18.1\% plaintext chunks in
%%the experimental VM dataset.

\section{Summary of Contributions}

We summarize the main contributions of the paper. 
%
\begin{itemize}[leftmargin=*]
\item
We present two novel frequency analysis attacks against encrypted
deduplication.  In addition to exploiting the leakage of frequencies due to
the deterministic nature of encrypted deduplication, both attacks exploit the
characteristics of deduplication workloads to increase the severity of
frequency analysis.
\item
We evaluate our frequency analysis attacks with several real-world datasets,
including long-term backups \cite{sun16,FSL14}, Windows file system snapshots
\cite{meyer11}, and VM disk images \cite{li15,qin17}.  We present new
observations based on our evaluation, and further analyze the security
implications of how our frequency analysis attacks bring actual damages. 
\item 
We discuss possible countermeasures to mitigate the information leakage in
encrypted deduplication.  
\end{itemize}

The remainder of the paper proceeds as follows. 
Section~\ref{sec:background} presents the basics of encrypted deduplication.
Section~\ref{sec:threat} defines the threat model. 
Sections~\ref{sec:distribution-attack} and \ref{sec:clustering-attack}
present two new frequency analysis attacks against encrypted deduplication.
Section~\ref{sec:experiment} presents our trace-driven evaluation results.
Section~\ref{sec:countermeasure} discusses the countermeasures against
information leakage. Section~\ref{sec:related} reviews related work, and
finally, Section~\ref{sec:conclusion} concludes the paper.

%under a precision of 76.8\%.

% \begin{table}
% 	\centering
% \caption{Summary of inference attacks against encrypted deduplication}
% 	\vspace{-3pt}
% 	\small
% 	\begin{tabular}{@{}p{2.15cm}p{1.2cm}p{.3cm}p{.5cm}p{1.1cm}l@{}}
% \toprule
% \multirow{2}{*}{\bf Objectives} & \multicolumn{3}{c}{\bf Exploiting Leakages} & \multirow{2}{*}{\bf Chunking} & \multirow{2}{*}{\bf Where} \\ \cmidrule{2-4}
% 				  &   {\bf Frequency}    &   {\bf Size}    &   {\bf Order}   &                   &                   \\
% \midrule
% File Existence &       &  \checkmark  &      & Var-size                  & \cite{ritzdorf16} \\ 
% 	Chunk Recovery &  \checkmark  &  \checkmark  &      & Var-size                  & Section~\ref{sec:bucket_attack} \\ 
% 	Chunk Recovery &  \checkmark  &    &   \checkmark  & All                  & \cite{li17}, Section~\ref{sec:distribution_attack} \\ 
% 	Content Recovery &  \checkmark  &    &   Relax  & All                  & Section~\ref{sec:two_stage_attack} \\ 
%  \bottomrule
% \end{tabular} \medskip

% Note: we do not include (i) frequency analysis due to its low severity \cite{li17} and (ii) side-channel attack \cite{mulazzani11,halevi11,harnik10} as it only occurs in client-side and cross-user deduplication.
% \end{table}

\chapter{Background}
\label{sec:background}

In this section, we present the basics of both plain and encrypted
deduplication approaches. 
% We motivate why encrypted deduplication remains
% vulnerable.

\begin{figure}[t]
\centering
\includegraphics[width=.48\textwidth]{pic/dedup-view.pdf}
\caption{Overview of  deduplication workflow.}
\label{fig:dedup-view}
\end{figure}

We focus on {\em chunk-based deduplication}, which operates at the granularity
of small-size data units called {\em chunks}.  Figure~\ref{fig:dedup-view}
summarizes the deduplication workflow.  Specifically, a storage system first
partitions a file (e.g., backup) of a client into {\em logical chunks} via
some {\em chunking} procedure, such that each logical chunk is uniquely
identified by the cryptographic hash of its content called a {\em tag} (a.k.a.
fingerprint).  Two logical chunks are said to be {\em identical} if they have
the same tag, while the likelihood that distinct logical chunks have the same
tag is practically negligible \cite{black06}.  The storage system stores only
a copy of identical logical chunks as a {\em physical chunk}, and each
identical logical chunk refers to the same physical chunk via small-size
references.

Chunk-based deduplication is more fine-grained than whole-file deduplication,
and hence has higher storage efficiency in general.  We can further choose
either {\em fixed-size} or {\em variable-size} chunking for deduplication.
Fixed-size chunking partitions file data into equal-size (logical) chunks,
while variable-size chunking (a.k.a. content-defined chunking) often specifies
chunk boundaries in a content-dependent manner (e.g., via Rabin fingerprinting
\cite{rabin81}) and partitions file data into variable-size chunks.
Fixed-size chunking is simple and fast, while variable-size chunking maintains
storage efficiency in the face of content shifts since the majority of chunks
remain unchanged even the file has added or removed some content.
Variable-size chunking is often used in backup systems (e.g.,
\cite{zhu08,lillibridge09}), yet fixed-size chunking is shown to be effective
for some workloads (e.g., VM images \cite{jin09}).  Our work addresses both
fixed-size and variable-size chunking approaches.

{\em Encrypted deduplication} addresses chunk confidentiality in an
outsourcing environment (e.g., cloud storage), while preserving deduplication
effectiveness.  Traditional symmetric encryption requires that multiple
clients encrypt their file data by their (distinct) secret keys, thereby
transforming identical chunks into distinct encrypted chunks that can no
longer be deduplicated.  {\em Message-locked encryption (MLE)}
\cite{bellare13a} formalizes encrypted deduplication.  The baseline MLE
instantiation derives a symmetric key (called the {\em MLE key}) based on the
content of each {\em plaintext} (e.g., a logical chunk in chunk-based
deduplication), and encrypts the plaintext using the MLE key to form a {\em
ciphertext} (e.g., an encrypted logical chunk).  Thus, MLE ensures that
identical plaintexts are encrypted to identical ciphertexts.  Finally, the
storage system derives the tag from each ciphertext and performs
deduplication.

MLE can be realized as different instantiations (see Section~\ref{sec:related}). The
most popular one is convergent encryption (CE) \cite{douceur02}, which has
been implemented in a wide variety of storage systems (e.g., 
\cite{adya02,elephantdrive,mega,gnunet,freenet,cryptosphere,cox02,storer08,
anderson10}).  The main idea of CE is to derive the MLE key from the
cryptographic hash of the content of each plaintext.  Note that some MLE
instantiations \cite{bellare13a} allow identical plaintexts to be encrypted
into distinct ciphertexts.  Nevertheless, they ensure that the tags are still
derived from the plaintexts, so that they can perform deduplication by
checking the equality of tags.

Existing MLE instantiations all build on the notion {\em deterministic
encryption} to ensure that the ciphertexts (or the tags) are deterministically
derived from the plaintexts, so as to preserve deduplication effectiveness as
opposed to traditional symmetric encryption.  While deterministic encryption
provides confidentiality guarantees, in this paper, we argue that such a
deterministic nature can be exploited by an adversary to infer the original
plaintext from a given ciphertext.

%Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various practical systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}.

% from these distinct ciphertext chunks, and cannot detect whether the original content underlying these ciphertext chunks are identical.

% The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% For security concerns, users want their data to be encrypted before outsourcing.

% Figure~\ref{fig:dedup-view} presents an overview of {\em encrypted deduplication} \cite{bellare13a}, where multiple clients outsource data to a remote storage system that performs {\em deduplication} across  clients to save storage space. Specifically, each client first partitions file data into {\em logical chunks}, each of which is with either fixed or variable sizes. 
% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift.

% Then, the client protects each chunk via encryption. However, in traditional symmetric encryption, clients use their own (distinct) secret keys for encryption, and transform the same plaintext chunks to different ciphertext chunks. The storage system cannot detect whether the original content underlying these ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% % To save space, the storage system performs {\em deduplication} across all its users.

% Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$. We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks. Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift. Then, it removes duplicates in the graularity of chunk. In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.

% Deduplication is a technique that reduces storage space by eliminating content redundancies. Figure~\ref{fig:dedup-view} presents the logical view of a deduplication-enabled storage system, which operates at the granularity of {\em chunk} and removes the chunks that have identical content with some already stored chunks. 
% Specifically, it first partitions file data into an ordered sequence of {\em logical chunks}, each of which is with either fixed or variable sizes. 
% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift. Then, it only stores the chunks (called {\em physical chunks}) that have unique content, and refers other copies of a stored chunk via small-size references.

% Encrypted deduplication aims to address the chunk-level confidentiality of deduplication in an outsourcing environment (e.g., cloud storage). Consider a scenario where multiple users outsource storage to a remote third-party cloud service, which apply deduplication across its users to save storage space. For security concerns, users want their data to be encrypted before outsourcing. However, in traditional symmetric encryption, users use their own (distinct) secret keys for encryption, and  transform the same plaintext chunks to different ciphertext chunks. The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% {\em Message-locked encryption (MLE)} \cite{bellare13a} is a cryptographic primitive to achieve encrypted deduplication. It derives a symmetric key $K_M$ (called {\em MLE key}) based on the content of each message $M$ (e.g., $K_M$ is the cryptographic hash of $M$ \cite{douceur02}), and further uses the MLE key $K_M$ to encrypt $M$. This makes the ciphertext only depend on the plaintext, from which it is encrypted. The server can detect duplicates by checking the equality of ciphertexts (e.g., comparing their cryptographic hashes). Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}  for encrypted deduplication.

% Consider a scenario where multiple users outsource storage to a remote third-party cloud service. To save space, the cloud server performs {\em deduplication} across all its users. Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$. We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks. Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift. Then, it removes duplicates in the graularity of chunk. In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.

% that have the same fingerprint are {\em identical}, since the probability of fingerprint collision (i.e., different chunks lead to the same fingerprint) is negligible in practice \cite{black06}. A deduplication system stores only a single copy of identical chunks, while referring the other copies by small-size references.

% It performs chunking to partition input data into fixed-size or variable-size chunks. Fixed-size chunking generates all chunks that have a uniform chunk size; on the other hand, variable-size chunking, configured by the maximum, average and minimum chunk sizes, defines the boundary of each chunk (e.g., via Rabin fingerprinting \cite{rabin81}) through matching a specific content pattern. This makes it robust against content shift.

% \subsection{Leakage Channels}
% \label{sec:leakage}

% MLE applies {\em deterministic encryption}, and exposes some information, called {\em leakage}, about plaintext chunks. The fundamental leakage is {\em chunk frequency}, which is the number of times that each plaintext chunk appears in the original file data. Although the frequency leakage has been acknowledged in prior works \cite{abadi13,bellare15,ritzdorf16,li17}, it is hard to be prevented, since this breaks the one-to-one mapping between plaintext and ciphertext chunks, and leads to the degradation of deduplication performance \cite{abadi13} or storage efficiency \cite{li17} (see \S\ref{sec:countermeasure}).

% sacrifices security and exposes some information,  
% that has been . Specifically, MLE encrypts identical plaintext chunks into identical ciphertext chunks, and hence leaks  We

% Additional leakages \cite{ritzdorf16, li17} have been explored due to the careless deployment of encrypted deduplication. First, some deduplication systems \cite{xia11,lillibridge09,zhu08} aim for high performance, and operate chunks in the same order that they appear in plaintext files; this exposes the {\em logical order}, based on which one can identify the position of each chunk in input files. Second, some practitioners \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage overhead, and do not pad ciphertext chunks with any additional data; this exposes the {\em chunk size}, since the ciphertext chunks have the same number of blocks with corresponding plaintext chunks.

>>>>

\documentclass[bachelor]{thesis-uestc}
%----文内引用符号
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\crefname{section}{§}{§§}
%----------

@@

\input{introduction}

%\thesisacknowledgement

\nocite{*}
\bibliographystyle{thesis-uestc}
\bibliography{reference}
